Modeling Intervention Strategies for United States TB Control

### 2014-02-08 in_progress/presentations/paper/draft.tex
updated 5.4 and looked at discussion/future work

\documentclass{amsart}
\usepackage[pdftex]{graphicx}
\usepackage{enumerate,placeins}
\graphicspath{{figures/}}

@@

\subsection{Agent Based Evaluation}
The Agent Based Model allowed the statistical properties of the system to be
analyzed and verified. In particular, they illustrated that the deterministic
Hill model provides a robust and consistent statistical measure of TB epidemic
behavior in the US conditions. We found that the distribution of incidence and
final population sizes were normal, with mean accurate to the deterministic
model and standard deviations given in table X, in the Appendix.

\section{Discussion}
These results confirm the hypothesis that curing incoming LTBI rates is a
necessary step towards elimination and indicate that it is a cost effective
option. 
\subsection{Future Work}
This work could be extended by examining different classes of interventions or
more accurately estimating intervention cost with the deterministic extended
Hill. Further work could also be done with the agent-based Hill Model, by using
it to examine the effect contact structure plays on US TB incidence levels or to
examine the effects drug-resistant TB will have on US TB dynamics. 
\section{Appendix}
\subsection{Hill Constants}
Below, we detail some of the relevant constants in the Basic Hill Model, and their best-fit
values. A full listing of constants used in the original Hill Model can be found in <CITATION HERE> 
\begin{figure}[h]
  \begin{center}
    \tiny{
    \begin{verbatim}
sigmaLBase  <- 0.057
fBase       <- 0.187
transBase   <- 1
incLTBIBase <- 1

>>>>

\documentclass{amsart}
\usepackage[pdftex]{graphicx}
\usepackage{enumerate,placeins}
\usepackage{color}
\graphicspath{{figures/}}

@@

\subsection{Agent Based Evaluation}
The agent-based model allowed the statistical properties of the system to be
analyzed and verified. In particular, it illustrated that the deterministic
Hill model provides a robust and consistent statistical measure of TB epidemic
behavior in the US conditions. We found that the distribution of incidence and
final population sizes were normal, with mean accurate to the deterministic
model and standard deviations given in table X, in the Appendix. Additionally,
the agent-based model provided a computational framework to produce
meaningful intervention results. On lab-grade, student hardware, a statistically
meaningful experiment could be run overnight, producing data in a day. This
demonstrates that this modeling strategy is feasible in this general case.

\section{Discussion}
These results confirm the hypothesis that curing incoming LTBI rates is a
necessary step towards elimination and indicate that it is a cost effective
option. \\
{\huge \color{red} Where did we show it was cost effective relative to other
interventions? Also, the section below (future work) might be better just
directly included in the discussion}\\
\subsection{Future Work}
This work could be extended by examining different classes of interventions or
more accurately estimating intervention cost with the deterministic extended
Hill. Further work could also be done with the agent-based Hill Model, by using
it to examine the effect contact structure plays on US TB incidence levels or to
examine the effects drug-resistant TB will have on US TB dynamics.

\section{Appendix}
\subsection{Hill Constants}
Below, we detail some of the relevant constants in the Basic Hill Model, and their best-fit
values. A full listing of constants used in the original Hill Model can be found in <CITATION HERE> 
\begin{figure}[h]
  \begin{center}
    \tiny{
    \begin{verbatim}
sigmaLBase  <- 0.057
fBase       <- 0.187
transBase   <- 1
incLTBIBase <- 1
